CLPFUDatabase: A suite of R packages for energy conversion chain analysis

### 2023-12-19 paper.Rmd
Better comments.
Completed the run

```{r, eval=TRUE}
library(devtools)
# (0) Use the metapackage to install all dependencies.
#     This package installation step is needed only once.
devtools::install_github("EnergyEconomyDecoupling/CLPFUDatabase")

@@

```{r}
# (5) Review results using the pins package.
#     Establish the pinboard.
pinboard <- file.path("ExampleFolder", "OutputData", "PipelineReleases") |> 
  pins::board_folder(versioned = TRUE)
#     Look at the psut data frame
#     created by the PFUDatabase pipeline.
psut <- pinboard |>
  pins::pin_read(name = "psut", version = "20231211T161342Z-3e2fb")
head(as.data.frame(psut), 2)
#     Each column of the psut data frame contains sparse matrices, 
#     the columns of which are suppressed on display.
#     Show the column names here.
colnames(psut$R[[1]])
#     Show an example resource (R) matrix.
psut$R[[1]]

>>>>

```{r, eval=FALSE}
library(devtools)
# (0) Use the CLPFUDatabase metapackage to install all dependencies.
#     This package installation step is needed only once.
devtools::install_github("EnergyEconomyDecoupling/CLPFUDatabase")

@@

```{r}
# (5) Review results using the pins package.
#     Establish the pinboard.
pinboard <- file.path("ExampleFolder", "OutputData", "PipelineReleases") |> 
  pins::board_folder(versioned = TRUE)
#     Look at the psut data frame
#     created by the PFUDatabase pipeline.
psut <- pinboard |>
  pins::pin_read(name = "psut", version = "20231219T204403Z-2c3ce")
head(as.data.frame(psut), 2)
#     Each column of the psut data frame contains sparse matrices, 
#     the columns of which are suppressed on display.
#     Show the column names here.
colnames(psut$R[[1]])
#     Show an example resource (R) matrix.
psut$R[[1]]
